\huge Tor's Usability for Censorship Circumvention

### 2016-04-23 pets2017-paper/pets2017-paper.tex
Normalize version numbering.
Tor has its own independent version numbers, so you can't say
"Tor 5.0.3". Don't mention the Tor Browser version number until we start
getting more detailed, in the background.

  \begin{abstract}
{Tor has grown beyond its original purpose as an anonymity tool and has 
become a widely-used censorship circumvention tool.
This is the first study to examine Tor's usability as a censorship circumvention tool.
We evaluate, redesign, and test the Tor 5.0.3 configuration interface by
placing users in simulated censorship environments, instruct them to use Tor
to circumvent censorship, and measuring their interactions with the interface.
A 16-participant qualitative user study identifies common user struggles while circumventing censorship.
We use the results as feedback to redesign the configuration interface.
A 124-participant quantitative user study tests the impact of our changes
to find that our changes results in a significant reduction 
in the spent configuring a connection, while maintaining the same rate of success. We
conclude with recommendations for changes to the current configuration interface and discuss
alternative configuration processes with different balances of risk, automation, and user input.}
\end{abstract}
  \keywords{User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

@@

We evaluate, redesign, and test the Tor 5.0.3 configuration interface by
measuring participants' interactions with the interface in various censorship environments.
The first user study is a small-scale, one-on-one experiment that collected 
behavioral patterns and failure cases with the interface through user observations
and interviews (Section~\ref{sec:qualitative}). This feedback was used to make changes to the interface (Section~\ref{redesign}). The second user study is a large-scale, data-centric user study
that collected data on user interactions with the interface to quantify the impact of the design changes (Section~\ref{sec:quantitative}).

@@

\section{Conclusion} 
We conducted a series of experiments to improve the Tor 5.0.3 Tor launcher configuration interface, which helps users circumvent censorship using Tor. The qualitative user study interviews 16 pre-screened participants about their experience trying to circumvent mild, intermediate, and heavy censorship with the current interface, giving insight into common challenges in configuring a connection, such as confusing the necessity of bridges and proxies, assuming that a correct configuration was wrong due to a progress bar bug, and not knowing what to do on failure. This feedback is used to guide the redesign of the configuration interface.

>>>>

  \begin{abstract}
{Tor has grown beyond its original purpose as an anonymity tool and has 
become a widely-used censorship circumvention tool.
This is the first study to examine Tor's usability as a censorship circumvention tool.
We evaluate, redesign, and test the Tor configuration interface by
placing users in simulated censorship environments, instruct them to use Tor
to circumvent censorship, and measuring their interactions with the interface.
A 16-participant qualitative user study identifies common user struggles while circumventing censorship.
We use the results as feedback to redesign the configuration interface.
A 124-participant quantitative user study tests the impact of our changes
to find that our changes results in a significant reduction 
in the spent configuring a connection, while maintaining the same rate of success. We
conclude with recommendations for changes to the current configuration interface and discuss
alternative configuration processes with different balances of risk, automation, and user input.}
\end{abstract}
  \keywords{User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

@@

We evaluate, redesign, and test the Tor configuration interface by
measuring participants' interactions with the interface in various censorship environments.
The first user study is a small-scale, one-on-one experiment that collected 
behavioral patterns and failure cases with the interface through user observations
and interviews (Section~\ref{sec:qualitative}). This feedback was used to make changes to the interface (Section~\ref{redesign}). The second user study is a large-scale, data-centric user study
that collected data on user interactions with the interface to quantify the impact of the design changes (Section~\ref{sec:quantitative}).

@@

\section{Conclusion} 
We conducted a series of experiments to improve the Tor Browser 5.0.3 configuration interface, which helps users circumvent censorship using Tor. The qualitative user study interviews 16 pre-screened participants about their experience trying to circumvent mild, intermediate, and heavy censorship with the current interface, giving insight into common challenges in configuring a connection, such as confusing the necessity of bridges and proxies, assuming that a correct configuration was wrong due to a progress bar bug, and not knowing what to do on failure. This feedback is used to guide the redesign of the configuration interface.
